|

### 2021-01-06 02-Chp-Background.Rmd
End of day: -3533
End of day: -3403

@@

###	Diagnosis
Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition. Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g. the Mini-Mental State Examination), to clinical tests (e.g. Magnetic Resonance Imaging (MRI) scans).

@@

@@

Historically, studies on dementia have faced a range of challenges. As a range of determinants (genetic, environmental and lifestyle) are thought to jointly influence the risk, progression and outcomes of dementia, any individual association is likely to have only a small effect. Therefore, the statistical power need to detect these associations will often require sample sizes that are unfeasible using primary data collection. 
This fact is further complicated by the long latency of dementia, which necessitates a costly long-term approach to patient follow-up. Furthermore, dementia studies often have limited generalisability to the target population, as certain subgroups (e.g. the very old) are frequently under-represented in study cohorts due to difficulties associated with their recruitment.9 Finally, studies employing a case-control design are further limited by the high potential for differential recall bias between those who have and have not developed dementia.10

@@

Include CIND definition here

@@

@@

@@

## Evidence synthesis

>>>>

This Chapter will provide an overview of the key exposures, outcomes and methods used throughout this thesis.

@@

###	Diagnosis
Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition (is this true, or would it be better to say that there is no gold standard test without an autopsy). Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g. the Mini-Mental State Examination), to clinical tests (e.g. Magnetic Resonance Imaging (MRI) scans).

### Criteria

Several scales are commonly used to diagnose dementia and associated diseases for research purposes. Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke–Alzheimer Disease and Related Disorders (NINCDS–ADRDA).[@dubois2007] [**Need first NINCDS-ADRDA citation and DSM- **]

**Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in Chapter \@ref(sys-rev-heading)**

@@

``` {r}
library(gt)
library(dplyr)

gt(data = mtcars) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = list(cells_body(
      columns = vars(mpg)),
      cells_column_labels(columns = vars(mpg))))

```

@@

Historically, studies on dementia have faced a range of challenges. As a range of determinants (genetic, environmental and lifestyle) are thought to jointly influence the risk, progression and outcomes of dementia, any individual association is likely to have only a small effect. Therefore, the statistical power need to detect these associations will often require sample sizes that are **unfeasible** using primary data collection. 
This fact is further complicated by the long latency of dementia, which necessitates a costly long-term approach to patient follow-up. Furthermore, dementia studies often have limited generalisability to the target population, as certain subgroups (e.g. the very old) are frequently under-represented in study cohorts due to difficulties associated with their recruitment.9 Finally, studies employing a case-control design are further limited by the high potential for differential recall bias between those who have and have not developed dementia.10

@@

*Cognitive impairment not dementia* (CIND) is another term used to described those with cognitivie impairment but who fall below the diagnostic criteria for dementia.

@@

The blood profile has a range of lipid fractions to it. However, for the sake of this thesis, we will only consider the three most important fractions, namely total cholesterol, low density lipoprotein cholesterol (LDLc), high density lipoprotein cholesterol (HDLc) and trigylcerides (TG).

@@

Include formula for working out total cholesterol and the ranges.

LDL-c levels are not directly measured but instead are estimated from using the Friedewald formula,[@friedewald1972] where the :

$$LDLc \approx TC - HDLc - kTG$$
where $k$ is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.

Limitations to the method include a requirement to fast for 12-14hrs prior to measures, an inability to estimate LDLc if TG levels are high

``` {block type='correction'}
Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters.
```

@@

### Evidence synthesis

### Primary cohort analysis

### 2021-01-06 04-Chp-Systematic-Review.Rmd
End of day: -3533
End of day: -3403

@@

* Check if there are protocols available for any of the published reports, and whether there were
* Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st

@@

>>>>

### Sources of heterogeneity

Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**

@@

* Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
* Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st

@@

Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [ALSO CITE WILKINSON AND MCGUINNESS HERE].

In addition, the a
